Disparate views of disparity

### 2017-12-11 Analysis/data_cleaning.Rmd
updated method compiler

## Distance
distances <- c("Gower distance", "Euclidean distance", "mean square euclidean distance", "Procrustes distances \\(geomorph\\)", "other distances", "Procrustes distances", "Average square distance", "mean distance", "mean euclidean distance", "mean Manhattan distance", "Euclidean distance between groups", "average squared distance", "mean euclidean distance", "Procrustes distance", "MNND \\(Mean nearest neighbour distance\\)", "Euclidean Procrustes distances", "sum of Procrustes distances", "range of maximum euclidean distance", "average Procrustes distance", "sum of the squared Procrustes distances")
disparity <- multi.gsub(distances, "distances", disparity)

@@

## Distance from centroid
centroids <- c("distance from centroids", "centroid", "Procrustes distances from centre", "distance from centroids", "distance from neighbour", "furthest distance", "Average square distance from centroid", "distance from centroid", "centroid size", "distance from centroid", "Group centroid", "mean distance from centroids", "mean distance to centroid", "mean Procrustes distance from centroid", "distances to centroids")
disparity <- multi.gsub(centroids, "centroids", disparity)

>>>>

## Distance
distances <- c("Gower distance", "Euclidean distance", "mean square euclidean distance", "Procrustes distances \\(geomorph\\)", "other distances", "Procrustes distances", "Average square distance", "mean distance", "mean euclidean distance", "mean Manhattan distance", "Euclidean distance between groups", "average squared distance", "mean euclidean distance", "Procrustes distance", "MNND \\(Mean nearest neighbour distance\\)", "Euclidean Procrustes distances", "sum of Procrustes distances", "range of maximum euclidean distance", "average Procrustes distance", "sum of the squared Procrustes distances", "distance from centroids", "centroid", "Procrustes distances from centre", "distance from centroids", "distance from neighbour", "furthest distance", "Average square distance from centroid", "distance from centroid", "centroid size", "distance from centroid", "Group centroid", "mean distance from centroids", "mean distance to centroid", "mean Procrustes distance from centroid", "distances to centroids")
disparity <- multi.gsub(distances, "distances", disparity)

@@

# ## Distance from centroid
# centroids <- c("distance from centroids", "centroid", "Procrustes distances from centre", "distance from centroids", "distance from neighbour", "furthest distance", "Average square distance from centroid", "distance from centroid", "centroid size", "distance from centroid", "Group centroid", "mean distance from centroids", "mean distance to centroid", "mean Procrustes distance from centroid", "distances to centroids")
# disparity <- multi.gsub(centroids, "centroids", disparity)

### 2017-12-11 Analysis/disparity_methods.Rmd
updated method compiler

```{r}
## Removed columns
removed_factors <- c(1)

@@

```{r, fig.width = 8, fig.height = 8}
## Get the variance per axis
scree_plot <- dispRity::variances(ordinated_data)
percentages_scree <- round(scree_plot/sum(scree_plot)*100, digit = 2)

@@

```{r}
cleaned_data <- readRDS("../Data/Processed/cleaned_data.Rda")

@@

```{r, fig.width = 8, fig.height = 8}
col_palette <- c("red", "blue", "green3", "grey")

@@

```{r}
## Creating the custom groups list
groups_list <- list("Claddis" = Claddis_group_id, "geomorph" = geomorph_group_id, "dtt" = dtt_group_id)

@@

```{r, fig.width = 12, fig.height = 12}
## Get the data for cumulative curves
total_cumulative <- data_raw[,c(1,3)]
#data_type_cumulative <- data_raw[,c(1,4)]

@@

```{r}
plot.data(fuzzy.sort.data(data[,1], factors[[1]]), proportion = TRUE, ylim = c(0, 100), main = names(factors)[[1]])
```

>>>>

```{r, eval = FALSE}
## Removed columns
removed_factors <- c(1)

@@

```{r, fig.width = 8, fig.height = 8, eval = FALSE}
## Get the variance per axis
scree_plot <- dispRity::variances(ordinated_data)
percentages_scree <- round(scree_plot/sum(scree_plot)*100, digit = 2)

@@

```{r, eval = FALSE}
cleaned_data <- readRDS("../Data/Processed/cleaned_data.Rda")

@@

```{r, fig.width = 8, fig.height = 8, eval = FALSE}
col_palette <- c("red", "blue", "green3", "grey")

@@

```{r, eval = FALSE}
## Creating the custom groups list
groups_list <- list("Claddis" = Claddis_group_id, "geomorph" = geomorph_group_id, "dtt" = dtt_group_id)

@@

```{r, fig.width = 12, fig.height = 12, eval = FALSE}
## Get the data for cumulative curves
total_cumulative <- data_raw[,c(1,3)]
#data_type_cumulative <- data_raw[,c(1,4)]

@@

```{r, eval = FALSE}
plot.data(fuzzy.sort.data(data[,1], factors[[1]]), proportion = TRUE, ylim = c(0, 100), main = names(factors)[[1]])
```
